%-----------------------------------------------------------------------
% Aditya Raj's Resume in sb2nov latex format
%-----------------------------------------------------------------------

\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\usepackage{fancyhdr}

% Ensure that page numbers are not shown
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

% Section formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands for bullet points and separation
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \textbf{#1} \hfill {#2} \\
    \textit{#3} \hfill {#4} \vspace{-2pt}
}
\newcommand{\resumeSubItem}[2]{\item\small{\textbf{#1}{: #2}}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%-------------------- Heading --------------------
\begin{center}
  {\Huge \scshape Aditya Raj} \\[1pt]
  Software Developer 2 | Backend \& Cloud Microservices Developer
\end{center}
\vspace{-10pt}
\vspace{4pt}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
  Greater Noida, India &
  \href{tel:+919811210024}{+91-9811210024} &
  \href{mailto:rajaditya.1710@gmail.com}{rajaditya.1710@gmail.com} \\
  \href{https://linkedin.com/in/rajaditya1710}{\faLinkedin\ linkedin.com/in/rajaditya1710} &
  \href{https://github.com/aditya-raj-1710}{\faGithub\ github.com/aditya-raj-1710} &
  \\
\end{tabular*}

%-------------------- Summary --------------------
\section{Summary}
\small{
Software Developer with 5 years of experience building scalable microservices on Oracle Cloud (OCI). Proficient in Java, Helidon, Spring Boot, Docker, and Kubernetes. Adept at optimizing application performance, leading cloud migrations, and integrating value-added features.
}

%-------------------- Skills ---------------------
\section{Core Skills}
\resumeItemListStart
  \resumeSubItem{Languages}{Java, SQL, Python, C++}
  \resumeSubItem{Frameworks}{Microservices, Helidon, Maven, Spring Boot}
  \resumeSubItem{Cloud \& Containers}{OCI, CI/CD, Docker, Kubernetes, AWS, Azure}
  \resumeSubItem{Data/Streaming}{Oracle DB, Oracle ADB, Apache Kafka}
  \resumeSubItem{Monitoring}{Prometheus, Grafana, Jaeger}
  \resumeSubItem{Tools \& Practices}{Git, GitLab, Jira, Confluence, REST APIs, Agile, Unit \& Integration Testing, Cline \& MCP server}
\resumeItemListEnd

%-------------------- Experience -----------------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Oracle Financial Services Software Limited}{Bangalore}
  {Application Developer 2 | Backend Engineer}{Sep 2022 -- Present}
\resumeItemListStart
  \resumeItem{Led Agile team tasks for critical release cycles and project milestones.}
  \resumeItem{Developed orchestrator components increasing performance and reliability, adopted company-wide.}
  \resumeItem{Optimized SQL queries and backend modules, enhancing throughput for datasets of 50M+ records.}
  \resumeItem{Integrated and designed new cloud-native features, improving product capabilities and scalability.}
  \resumeItem{Engineered and delivered FTP Engine workflow for ALMCS product suite.}
  \resumeItem{Utilized Oracle Code Assist, Cline, and MCP servers to streamline and automate code pipelines.}
  \resumeSubItem{Tech Used}{Helidon, Java, Maven, Oracle ADB, Docker, Kubernetes, OCI, Prometheus, Jaeger, Grafana}
\resumeItemListEnd

\resumeSubheading
  {Oracle Financial Services Software Limited}{Bangalore}
  {Associate Application Developer}{Sep 2020 -- Aug 2022}
\resumeItemListStart
  \resumeItem{Pioneered Conditional Assumption approach, delivering 10x speedup versus legacy solutions.}
  \resumeItem{Migrated complex on-premise systems into cloud-native microservices architecture.}
  \resumeItem{Executed comprehensive unit, integration, and load testing for all critical CI/CD deployments.}
  \resumeItem{Refactored legacy codebase; coordinated integration with cross-functional teams.}
  \resumeSubItem{Tech Used}{Java, Scala, Oracle DB, Maven, Spring Boot, Microservices, Docker, Kubernetes, OCI}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- Education ------------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Malaviya National Institute of Technology Jaipur}{Jul 2016 -- May 2020}
    {Bachelor of Technology, Electronics \& Communication Engineering | GPA: 7.65}{}
\resumeSubHeadingListEnd

%-------------------- Projects -------------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {Stock Ticker Data Fetcher}{Jun 2025 -- Aug 2025}
    {Python, Snowflake, Polygon.io API}{}
  \resumeItemListStart
    \resumeItem{Built real-time ETL pipeline in Python to fetch, process, and store U.S. stock ticker data with both daily and ad-hoc scheduling.}
    \resumeItem{Integrated Snowflake for automated data warehousing and advanced analytics.}
    \resumeItem{Implemented robust logging and error handling with detailed monitoring.}
    \resumeItem{\href{https://github.com/aditya-raj-1710/stock-trading-python-app}{\faGithub\ View on GitHub}}
  \resumeItemListEnd
  \resumeSubheading
    {Facial Recognition Attendance System}{Sep 2019 -- May 2020}
    {Academic Project, Machine Learning}{}
  \resumeItemListStart
    \resumeItem{Engineered a computer vision solution using facial recognition to automate student attendance.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%------------------- Achievements ----------------
\section{Awards \& Achievements}
\resumeItemListStart
  \resumeItem{Oracle Cloud Infrastructure 2025 Generative AI Professional}
  \resumeItem{Oracle Cloud Infrastructure 2024 Certified Foundations Associate}
  \resumeItem{FSGBU Pacesetter Award (Apr 2023 -- Mar 2024), Oracle Financial Services}
  \resumeItem{Best Team Award (Apr 2023 -- Mar 2024), Oracle Financial Services}
  \resumeItem{CODEFORCES Pupil (Max Rating 1300+); 500+ problems solved across platforms}
  \resumeItem{Volunteered at Sphinx, Rajasthan's largest TechFest (25K+ attendees)}
\resumeItemListEnd

\end{document}
